---
title: "Part3"
output: html_document
---

```{r,echo=FALSE, include=FALSE}
library(dplyr)
library(tidyverse) 
library(broom)
library(gridExtra)
library(car)
library(patchwork)
library(MASS)
data1=read.csv("heart_failure_clinical_records_dataset.csv")
heart_failure <- data1 %>% mutate(Smoke = ifelse(data1$smoking == "1","Yes","No"))
heart_failure <- heart_failure %>% mutate(Sex = ifelse(data1$sex == "1","Male","Female"))
heart_failure <- heart_failure %>% mutate(High_blood_pressure = ifelse(data1$high_blood_pressure == "1","Yes","No"))
heart_failure <- heart_failure %>% mutate(Diabetes = ifelse(data1$diabetes == "1","Yes","No"))
heart_failure <- heart_failure %>% mutate(Anaemia = ifelse(data1$anaemia == "1","Yes","No"))
```

## Training and Testing data
```{r}
set.seed(697)
n <- nrow(heart_failure)
training_indices <- sample(1:n, size= round(0.80*n))
heart_failure <- heart_failure %>% rowid_to_column()
train <- heart_failure %>% filter(rowid %in% training_indices)
test <- heart_failure %>% filter(!(rowid %in% training_indices))
```

##Numerical variable 



```{r}
box_ejection_fraction <- train %>%
ggplot(aes(y=ejection_fraction)) +
geom_boxplot(color='black', fill= 'steelblue') +
labs(title="Ejection Fraction")

```

```{r}
box_platelets <- train %>%
ggplot(aes(y=platelets)) +
geom_boxplot(color='black', fill= 'steelblue') +
labs(title="Platelets ")

```

```{r}
plot(train$ejection_fraction ~ train$platelets, main=" Ejection Fraction vs Platelets ", xlab="Platelets", ylab="Ejection Fraction")
```

```{r}
box_serum_creatinine <- train %>%
ggplot(aes(y=serum_creatinine)) +
geom_boxplot(color='black', fill= 'steelblue') +
labs(title="Serum Creatinine ")

```

```{r}
plot(train$ejection_fraction ~ train$serum_creatinine, main=" Ejection Fraction vs Serum Creatinine ", xlab="Serum Creatinine", ylab="Ejection Fraction")
```

```{r}
box_creatinine_phosphokinase <- train %>%
ggplot(aes(y=creatinine_phosphokinase)) +
geom_boxplot(color='black', fill= 'steelblue') +
labs(title="Creatinine Phosphokinase ")

```

```{r}
plot(train$ejection_fraction ~ train$creatinine_phosphokinase, main=" Ejection Fraction vs Creatinine Phosphokinase ", xlab="Creatinine Phosphokinase", ylab="Ejection Fraction")
```

```{r}
box_Age <- train %>%
ggplot(aes(y=age)) +
geom_boxplot(color='black', fill= 'steelblue') +
labs(title="Age")

```

```{r}
plot(train$ejection_fraction ~ train$age, main=" Ejection Fraction vs Age ", xlab="Age", ylab="Ejection Fraction")
```

## Summary Numerical 
```{r}
(box_ejection_fraction | box_platelets | box_serum_creatinine) /
(box_creatinine_phosphokinase | box_Age)
```

```{r}
par(mfrow = c(2, 2))
plot(train$ejection_fraction ~ train$platelets, main=" Ejection Fraction vs Platelets ", xlab="Platelets", ylab="Ejection Fraction")
plot(train$ejection_fraction ~ train$serum_creatinine, main=" Ejection Fraction vs Serum Creatinine ", xlab="Serum Creatinine", ylab="Ejection Fraction")
plot(train$ejection_fraction ~ train$creatinine_phosphokinase, main=" Ejection Fraction vs Creatinine Phosphokinase ", xlab="Creatinine Phosphokinase", ylab="Ejection Fraction")
plot(train$ejection_fraction ~ train$age, main=" Ejection Fraction vs Age ", xlab="Age", ylab="Ejection Fraction")
```




```{r}
summary(train$ejection_fraction)
summary(train$platelets)
summary(train$serum_creatinine)
summary(train$creatinine_phosphokinase)
summary(train$age)

```


## Calaterical 
```{r}
bar_anaemia <- train %>%
ggplot(aes(x=Anaemia)) +
geom_bar(color='black', fill='steelblue') +
labs(title="Anaemia") +
coord_flip()
```

```{r}
bar_high_blood_pressure <- train %>%
ggplot(aes(x=High_blood_pressure)) +
geom_bar(color='black', fill= 'steelblue') +
labs(title="High Blood Pressure") +
coord_flip()
```

```{r}
bar_sex <- train %>%
ggplot(aes(x=Sex)) +
geom_bar(color='black', fill= 'steelblue') +
labs(title="Sex") +
coord_flip()
```

```{r}
bar_smoking <- train %>%
ggplot(aes(x=Smoke)) +
geom_bar(color='black', fill= 'steelblue') +
labs(title="Smoking") +
coord_flip()
```

```{r}
bar_diabetes <- train %>%
ggplot(aes(x=Diabetes)) +
geom_bar(color='black', fill= 'steelblue') +
labs(title="Diabetes") +
coord_flip()
```

```{r}
table(train$Anaemia)
table(train$Smoke)
table(train$High_blood_pressure)
table(train$Diabetes)
table(train$Sex)
```


## Summary Cate

```{r}
(bar_anaemia | bar_high_blood_pressure | bar_diabetes) /
(bar_sex | bar_smoking) 
```




##full model 
## Set the model 
```{r}
full_model <- lm(ejection_fraction ~ platelets + serum_creatinine + creatinine_phosphokinase + age + Anaemia + High_blood_pressure + Sex + Smoke + Diabetes, data = train)
```


```{r}
vif(full_model)
```


## Condiction1 and Condiction2 

```{r}
#condition 1 
yhat <- fitted(full_model)
yi <- train$ejection_fraction
ggplot()+geom_point(aes(y=yhat,x=yi))+ylim(20,80)
```

```{r}
#condition 2
pairs(~platelets + serum_creatinine + creatinine_phosphokinase + age, data=train)
```

##Drew the Residual Plot

```{r}
res <- rstandard(full_model)
y_hat <- fitted(full_model)
plot(y_hat, res)
```


```{r}
## Residual vs. Predictors
par(mfrow = c(3, 3))
res <- rstandard(full_model)
y_hat <- fitted(full_model)
plot(y_hat, res)
plot(train$platelets, res)
plot(train$serum_creatinine, res)
plot(train$creatinine_phosphokinase, res)
plot(train$age, res)
qqnorm(res)
qqline(res)
```

##qq plot full model 
```{r}
qqnorm(res)
qqline(res)
```

## outlier

```{r}
r <- rstandard(full_model)
out <- which(r > 2 | r < -2)
out

```

##leverage points

```{r}
h <- hatvalues(full_model)
threshold <- 2 * (length(full_model$coefficients)/nrow(train))
w <- which(h > threshold)
train[w,]

```

```{r}
D <- cooks.distance(full_model)
cutoff <- qf(0.5, length(full_model$coefficients), nrow(train)-length(full_model$coefficients), lower.tail=T)
which(D > cutoff)
fits <- dffits(full_model)
```


## Summary full model 
```{r}
summary(full_model)
```




## 为什么用 random selection

## reduce model 
## AIC Select Reduce Model
```{r}
stepAIC(lm(ejection_fraction ~ platelets + serum_creatinine + creatinine_phosphokinase + age + Anaemia + High_blood_pressure + Sex + Smoke + Diabetes,data=train), direction = "both", k=2)
```

##Set reduce model 
```{r}
reduce_model <- lm(ejection_fraction ~ platelets + Sex + Diabetes, data = train)
```


```{r}
summary(reduce_model)
```

```{r}
#condition 1 
yhat <- fitted(reduce_model)
yi <- train$ejection_fraction
ggplot()+geom_point(aes(y=yhat,x=yi))+ylim(15,80)
```
##Condiction2 (Since full model is satisfy, the reduce model also satisfy.)


```{r}
vif(reduce_model)
```

##Drew the Residual Plot 

```{r}
res <- rstandard(reduce_model)
y_hat <- fitted(reduce_model)
plot(y_hat, res)
```


```{r}
## Residual vs. Predictors
plot(train$platelets, res)
```

```{r}
par(mfrow=c(2,2))
res <- rstandard(reduce_model)
y_hat <- fitted(reduce_model)
plot(y_hat, res)
plot(train$platelets, res)
qqnorm(res)
qqline(res)
```

```{r}
r <- rstandard(reduce_model)
out <- which(r > 2 | r < -2)
out
```

```{r}
h <- hatvalues(reduce_model)
threshold <- 2 * (length(reduce_model$coefficients)/nrow(train))
w <- which(h > threshold)
train[w,]

```

```{r}
D <- cooks.distance(reduce_model)
cutoff <- qf(0.5, length(reduce_model$coefficients), nrow(train)-length(reduce_model$coefficients), lower.tail=T)
which(D > cutoff)
fits <- dffits(reduce_model)
```

##F-test (reduce model is better)

```{r}
anova(reduce_model,full_model)
```


```{r}
AIC(full_model)
AIC(reduce_model)
summary(full_model)$adj.r.squared
summary(reduce_model)$adj.r.squared
BIC(full_model)
BIC(reduce_model)
```


```{r}
#influencial points for auto_model:
D_auto <- cooks.distance(reduce_model)
cutoff_auto <- qf(0.5, length(reduce_model$coefficients), nrow(train)-length(reduce_model$coefficients), lower.tail=T)
which(D_auto > cutoff_auto)
```


## Get the test Model 

```{r}
test_model <- lm(ejection_fraction ~ platelets + Sex + Diabetes, data = test)
```

```{r}
vif(test_model)
```


```{r}
#condition 1 
yhat <- fitted(test_model)
yi <- test$ejection_fraction
ggplot()+geom_point(aes(y=yhat,x=yi))+ylim(30,40)
```

##condiction2 

##residual plot 
```{r}
res <- rstandard(test_model)
y_hat <- fitted(test_model)
plot(y_hat, res)
```

```{r}
## Residual vs. Predictors
plot(test$platelets, res)
```


```{r}
par(mfrow=c(2,2))
res <- rstandard(test_model)
y_hat <- fitted(test_model)
plot(y_hat, res)
plot(test$platelets, res)
qqnorm(res)
qqline(res)
```

```{r}
summary(test_model)
```

## estimate similar. 
 
```{r}
r <- rstandard(test_model)
out <- which(r > 2 | r < -2)
out

```

```{r}
h <- hatvalues(test_model)
threshold <- 2 * (length(test_model$coefficients)/nrow(train))
w <- which(h > threshold)
train[w,]

```

```{r}
D <- cooks.distance(test_model)
cutoff <- qf(0.5, length(test_model$coefficients), nrow(train)-length(test_model$coefficients), lower.tail=T)
which(D > cutoff)
fits <- dffits(test_model)
```


```{r}
#predict
pred <- predict(test_model, test)
pred 
```

```{r}
plot(pred ~ test$ejection_fraction)
```





